Stylistic Context Clustering for Token-Level Author Diarization

### 2017-08-30 paper/paper.tex
Made the paper a bit shorter

Let $l$ be a function that associates lengths in characters to segments. Specially, $l(\{\}) = 0$. For notational convenience, we also use $l$ to denote the sum of lengths of all segments in a set of segments: $l(S) = \sum_{s\in S} l(s),$ where $S$ is as set of segments. Given a document $D$, let $S_\mathrm{p} \subseteq \sigma(D)$ be a set of all true plagiarism segments of the document and $\hat{S}_\mathrm{p} \subseteq \hat{\sigma}(D)$ the segments predicted as plagiarism by the  model. With ${S_\mathrm{tp} = \bigcup_{(s,\hat{s})\in S_\mathrm{p}\times\hat{S}_\mathrm{p}} l(s\cap\hat{s})}$, the micro-averaged evaluation measures for intrinsic plagiarism detection are defined as follows:
\begin{align}
P_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(\hat{S}_\mathrm{p})}, \\
R_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
F_\mathrm{\mu} &= 2(P_\mathrm{\mu}^{-1}+R_\mathrm{\mu}^{-1})^{-1}.
\end{align}
The macro-average evaluation measures treat all plagiarism segments as equally important and are not affected by their lengths:
\begin{align}
P_\mathrm{M} &= \frac{1}{|\hat{S}_\mathrm{p}|}
	\sum_{\hat{s}\in\hat{S}_\mathrm{p}}
		\frac{{\sum_{s\in S_\mathrm{p}} l(s\cap\hat{s})}}{l(\hat{s})}, \\
R_\mathrm{M} &= \frac{1}{|S_\mathrm{p}|}
	\sum_{\hat{s}\in S_\mathrm{p}}
		\frac{{\sum_{s\in \hat{S}_\mathrm{p}} l(s\cap\hat{s})}}{l(s)}, \\
F_\mathrm{M} &= 2(P_\mathrm{M}^{-1}+R_\mathrm{M}^{-1})^{-1}.
\end{align}

@@

\paragraph{Basic feature extraction.} 
We define the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i+cs}\setminus\{t_i\}$ where $cs$ is a context size. From each context we extracted the most used stylometric features which we found in previous work. The features that we have considered in our models are:
\begin{itemize}
	\item \emph{Character tri-grams}. Frequencies of $n$-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}. They are able to capture lexical and contextual information, use of punctuation and errors which can be an author's "fingerprint". This feature is also tolerant to noise. Based on work by \citet{stamatatos-2009a} and \citet{rahman-2015}, we choose $n=3$. Maximal dimension of this feature vector was set to $200$.
	\item \emph{Stop words}. According to \citet{stamatatos-2009a}, sometimes also called \emph{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others. They are used unconsciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}. We used frequencies of $156$ English stop words available in NLTK.
	\item \emph{Special characters}. We used counts of all character sequences which satisfied a regular expression defined as \verb/[^\\w]{1,4}/. Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habits.
	\item \emph{POS tag counts}. This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}. We used all $12$ tags from the universal tag set available in NLTK.
	\item \emph{Average token length}. Used by \citet{kuznetsov-2016}, \citet{sittar-2016},  \citet{brooke-2012} and \citet{stein-2011}. \citet{koppel-2009} characterized this feature as a complexity measure.
	\item \emph{Bag of Words}. Bag of words text representation more captures content, rather than style \citep{stamatatos-2009a}. We included this feature because it boosted performance of our initial testing, even without words been previously stemmed or lemmatized (stop words were excluded). Counts of a maximum of 100 unigrams were used.
	\item \emph{Type-token ratio}\footnote{We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and its impact on final results was unknown to us.}. This feature is the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.
\end{itemize}

>>>>

Let $l$ be a function that associates lengths in characters to segments. Specially, $l(\{\}) = 0$. For notational convenience, we also use $l$ to denote the sum of lengths of all segments in a set of segments: $l(S) = \sum_{s\in S} l(s),$ where $S$ is as set of segments. Given a document $D$, let $S_\mathrm{p} \subseteq \sigma(D)$ be a set of all true plagiarism segments of the document and $\hat{S}_\mathrm{p} \subseteq \hat{\sigma}(D)$ the segments predicted as plagiarism by the  model. With ${S_\mathrm{tp} = \bigcup_{(s,\hat{s})\in S_\mathrm{p}\times\hat{S}_\mathrm{p}} l(s\cap\hat{s})}$, the micro-averaged evaluation measures for intrinsic plagiarism detection are defined as follows:
\begin{align}
P_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(\hat{S}_\mathrm{p})}, \\
R_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
F_\mathrm{\mu} &= 2(P_\mathrm{\mu}^{-1}+R_\mathrm{\mu}^{-1})^{-1}.
\end{align}
The macro-average evaluation measures treat all plagiarism segments equally regardless of their lengths:
\begin{align}
P_\mathrm{M} &= \frac{1}{|\hat{S}_\mathrm{p}|}
	\sum_{\hat{s}\in\hat{S}_\mathrm{p}}
		\frac{{\sum_{s\in S_\mathrm{p}} l(s\cap\hat{s})}}{l(\hat{s})}, \\
R_\mathrm{M} &= \frac{1}{|S_\mathrm{p}|}
	\sum_{\hat{s}\in S_\mathrm{p}}
		\frac{{\sum_{s\in \hat{S}_\mathrm{p}} l(s\cap\hat{s})}}{l(s)}, \\
F_\mathrm{M} &= 2(P_\mathrm{M}^{-1}+R_\mathrm{M}^{-1})^{-1}.
\end{align}

@@

\paragraph{Basic feature extraction.} 
We define the context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i+cs}\setminus\{t_i\}$ where $cs$ is context size. Based on previous work, we extract the most useful stylometric features from each context. The features considered in our models are:
\begin{itemize}
	\item \emph{Character tri-grams}. Frequencies of $n$-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}. They are able to capture lexical and contextual information, use of punctuation and errors which can be an author's "fingerprint". This feature is also tolerant to noise. Based on work by \citet{stamatatos-2009a} and \citet{rahman-2015}, we choose $n=3$. Maximal dimension of this feature vector was set to $200$.
	\item \emph{Stop words}. According to \citet{stamatatos-2009a}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others. They are used unconsciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}. We used frequencies of $156$ English stop words available in NLTK.
	\item \emph{Special characters}. We used counts of all character sequences which satisfied the following regular expression: \verb/[^\\w]{1,4}/. Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habits.
	\item \emph{POS tag counts}. This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}. We used all $12$ tags from the universal tag set available in NLTK.
	\item \emph{Average token length}. Used by \citet{kuznetsov-2016}, \citet{sittar-2016},  \citet{brooke-2012} and \citet{stein-2011}. \citet{koppel-2009} characterized this feature as a complexity measure.
	\item \emph{Bag of Words}. Bag of words text representation more captures content, rather than style \citep{stamatatos-2009a}. We include this feature because it boosted performance in our initial testing. Counts of at most 100 unigrams are used.
	\item \emph{Type-token ratio}\footnote{We wanted to use this feature to measure the vocabulary richness, but after we have evaluated performance, we realized that there was a bug in our implementation. The inpact on the results is unknown to us.}. This feature is the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.
\end{itemize}
